### 2025-03-05 tutorials/getstarted.qmd
avoid the modulo propsed in the PR but still mention the periodicity.

where we already represent all possible rotations when restricting $α$ to $[0,2π]$.
Adding two matrices $R_α + R_β$ does not yield a valid rotation matrix again, but we
can have these matrices in mind as being “locally like the real line”, since changing the rotation angle
slightly yields rotation matrices that are “close by” in the sense that they perform nearly the same rotation
when applied to a point $x ∈ ℝ^2$ by computing $R_αx$.
Matrix multiplication $R_β = R_{α_1} R_{α_2}$ does yield a new rotation and also fulfills all other
properties to yield a group operation. Using trigonometric identities we observe that $β = α_1 + α_2$.

>>>>

where we already represent all possible rotations when restricting $α$ to $[0,2π]$.
Adding two matrices $R_α + R_β$ does not yield a valid rotation matrix again, but we
can have these matrices in mind as being “locally like the real line”, since changing the rotation angle
slightly yields rotation matrices that are “close by” in the sense that they perform nearly the same rotation
when applied to a point $x ∈ ℝ^2$ by computing $R_αx$.
Matrix multiplication $R_β = R_{α_1} R_{α_2}$ does yield a new rotation and also fulfills all other
properties to yield a group operation.
Using trigonometric identities we observe that $R_β = R_{α_1+α_2}$.
Since the angle of rotation is $2π$-periodic, we also see here, that e.g. for small angles around $0$,
this behaves like the real line, but globally it differs, since $R_{α} = R_{α+2π}$
